---
title: "TIDYVERSE EXTEND"
author: "Jiho Kim"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Source: [Kagle data - Data Analysis Jobs, Based on NYC Jobs - October 2021](https://www.kaggle.com/intelai/data-analysis-jobs?select=data_analysis_jobs.csv)

This dataset contains current job postings available on the City of New York’s official jobs site ( http://www.nyc.gov/html/careers/html/search/search.shtml ). Internal postings available to city employees and external postings available to the general public are included.


## Load Packages
```{r}
library("tidyverse")
library("reactable")
```



## Data Set

The `readr package` in tidyverse library contains the function `read_csv` that will import data from a csv file. The csv file was downloaded from Kaggle.com dataset on Data Analysis Jobs in NYC for October 2021. The imported data was read in to RStudio as a dataframe, `da`.  
```{r}
da <- read_csv("https://github.com/candrewxs/Vignettes/blob/master/dadata/data_analysis_jobs.csv?raw=true")
```



Retrieve the names attribute of the da data set with the `names()` function.
```{r}
names(da)
```

## Group by Variables

### Dataset Question: How many job postings are Internal and External? What are the Levels and how many are available?

Create a new data frame using existing data frame (da) by extracting columns: Level and Posting Type. The `count()` combines `group_by` and `count rows in each group` into a single function. Renamed the column name "n" to "Count" and created an interactive data table. 
```{r}
plot1 <- da %>%
   count(Level, `Posting Type`)  # dplyr package: group and count 
colnames(plot1)[3] <- "Count" 
# use function colnames() to rename column 
# and access individual column names with colnames(df)[index]
reactable(plot1) # interactive data table
```

### Visualization 
```{r}
# discrete visualization with ggplot2
p1 <- ggplot(data = plot1) 
  p1 + geom_col(aes(Level, Count, fill = `Posting Type`))
```


### Dataset Question: What are the Business Titles categories which NYC hires Data Analysis to perform? Which Business Title has the highest demand for Data Analysis?

Create a new data frame using existing data frame (da) by extracting column: Business Title. Tidy data frame column to upper case and build a contingency table of the counts at each combination of factor levels with the `table()` function. Renamed the column name "pl2" to "Business Title" and created an interactive data table showing the frequency. 
```{r}
plot2 <- as.data.frame(da[,5])
plot2$`Business Title` <- toupper(plot2$`Business Title`)
pl2 <- as.data.frame(table(plot2))
colnames(pl2)[1] <- "Business Title"
reactable(pl2)
```


```{r}
summary(pl2) # calculates some statistics on the data
```

Filter Business Titles with a frequency greater or equal to 10.  
```{r}
pl_2 <- filter(pl2, Freq >= 10) 
pl_2
```

### Visualization 
```{r}
p2 <- ggplot(pl_2) 
  p2 + geom_col(aes(`Business Title`, Freq)) +
    coord_flip()
```

## Conclusion
Kagle data - Data Analysis Jobs, Based on NYC Jobs was loaded and analyzed using R base functions and packages from Tidyverse and Reactable. These are the Tidyverse packages that were utilized to load `(readr)` , perform data manipulation `(dplyr)` , create graphic representation of input data `(ggplot2)`.

## Extend

Using dplyr’s glimpse() function, we can take a look at the data as well as their types

```{r}
glimpse(da)
```

Using slice function to see specified row

```{r}
da%>%
  slice(1:7)
```

Using distinct function to see different level of position

```{r}
da %>% 
  distinct(Level) %>% 
  reactable(bordered = TRUE, striped = TRUE,
          highlight = TRUE, filterable = TRUE,  showPageSizeOptions = TRUE,
          showPagination = TRUE, pageSizeOptions = c(5, 10, 20),
          defaultPageSize = 5)
```

